---
title: "Data Analysis Lab 4: converting pcap files to csv, and analyze using Pandas"
author: "Justin Sallese"
date: "April 14, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Panda Code Origin](http://nbviewer.jupyter.org/url/dirk-loss.de/ipython-pandas-2013-05/pcap2.ipynb)

[Github Code](https://github.com/jsallese/Data-Analysis-Lab-4/blob/master/pandas.Rmd)

## Purpose: 

The purpose of this report is to determine the location of the orgin of the emails that are 
harrasing the proffesor.


## Preperation

```{r, message=FALSE, warning=FALSE}
setwd("~/pcap")
library(readr)
nitroba <- read_csv("nitroba")
head(nitroba)
```
## Data Description:

The first column is the packet number.

The second column is the time since the start of the data capture.

The third and fourth column is the source and destination IP address. 

The fifth column is the packet protocol type.

The sixth and seventh column are the length of the packet and the extra info of the packet.

## Nitroba University Harassment Scenario


## Packet Length Distribution

```{r Length Distribution}
Length = nitroba$Length
Frame_Num = nitroba$No.
plot(Frame_Num,
     Length, 
     col = "BLUE")
```

The above plot shows the distribution of the framelength throught the progression of the entirety of 
the data. This plot shows that there is a quite of bit of data above 1400, some below 400 and quite a
bit below 200. What this can tell us is that for certain types of packets have certain fixed lengths,
so if one knows the length of the type of packets you can know what type of packets where used at a 
glance. This plot is the same as the one genderated in the pandas code but with R code.

```{r Most Active Sources}
source = data.frame(head(summary(factor(nitroba$Source))))
colnames(source) <- c("count")
 q =barplot(source$count,
        main = "Most Active Source", 
        ylim = range(0:40000), 
        names.arg = rownames(source), 
        col = "BLUE", 
        width = 1,
        cex.names = .60,
        xlab = "IP Address",
        ylab = "Count")
 
 text(x = q, 
     y = source$count, 
     label = source$count, 
     pos = 3, cex = 0.9, col = "red")
```

Above is a graph of the top six most active source IP addresses.By looking at the first two source IP
addresses if the data is being captured during the time that the malicious emails are sent the first 
two most active source IP addresses are probably the attacker and the victim.

```{r Most Active Destination}
destination = data.frame(head(summary(factor(nitroba$Destination))))

colnames(destination) <- c("count")
 q =barplot(destination$count,
        main = "Most Active Destination", 
        ylim = range(0:42000), 
        names.arg = rownames(destination), 
        col = "BLUE", 
        width = 1,
        cex.names = .60,
        xlab = "IP Address",
        ylab = "Count")
 
 text(x = q, 
     y = destination$count, 
     label = destination$count, 
     pos = 3, cex = 0.9, col = "red")
```

Above is the most active destination IP addresses. By looking at the most active distination IP 
addresses and comparing them to the most active source IP addresses one can see that the first two 
most active IP addresses are the same. So if this where an official report to the proffesor that was 
getting harrased then the next steps that I would reccoment would be to first find out what was the 
proffesors IP address at the time and then investigate the next possible IP address and to gather 
data on the location and workspace of the prepetrator to catch them easier.

Conclusion: Assuming that the email harrasment has happended during the data capture the attacker 
either has an Ip address of 192.168.15.4 or an Ip address of 192.168.1.64. Furthur investigation 
other applications such as nmap and network miner are required.

